Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-12-02 paper/results.tex
increase size of captions in fig. 6 plots
increase size of fig. 3-5

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp1_slice0}
	\includegraphics[width=0.9\linewidth]{exp1_slice1}
	\includegraphics[width=0.9\linewidth]{exp1_slice2}
	\caption{\label{fig:exp1-time-vs-reg}Results of Experiment~1, 20~best-performing surrogates per each considered family, plotted in
		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) with 3~selected discrete feature assignments out
		of~4.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp2_time_vs_reg}
	\caption{\label{fig:exp2-time-vs-reg}Results of Experiment~2, plotted analogously
	to~\Fref{fig:exp1-time-vs-reg}.}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{scaling_metric_r2}
	\includegraphics[width=0.9\linewidth]{scaling_time_train}
	\includegraphics[width=0.9\linewidth]{scaling_time_pred}
	\caption{Results of the scaling benchmark displayed as a function of
	training set size. From top to bottom, regression performance (as $R^2$),
	mean training time and mean prediction time.}
	\label{fig:scaling}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model6_rasterized}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model7_rasterized}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model1_rasterized}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model3_rasterized}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model4_rasterized}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model5_rasterized}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model2_rasterized}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\includegraphics[width=\linewidth]{exp4_model8_rasterized}
	\end{minipage}

>>>>

\begin{figure}
	\centering
	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice0}

	\vfill

	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice1}

	\vfill

	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=10pt 15pt 10pt 10pt,clip,width=1.1\linewidth]{exp1_slice2}

	\caption{\label{fig:exp1-time-vs-reg}Experiment~1 results. 20~best surrogates per each considered family, plotted in
		terms of~$\overline{t}_{\text{pred.}}$ and~$R^2$ with 3~selected slices out
		of~4.}
\end{figure}

@@

\begin{figure}
	\centering

	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=10pt 15pt 10pt 10pt,clip,width=1.1\linewidth]{exp2_time_vs_reg_edited}
	\caption{\label{fig:exp2-time-vs-reg}Experiment~2 results, plotted analogously
	to~\Fref{fig:exp1-time-vs-reg}.}
\end{figure}

@@

\begin{figure}
	\centering
	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=10pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_metric_r2}

	\vfill

	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=5pt 50pt 10pt 10pt,clip,width=1.1\columnwidth]{scaling_time_train}

	\vfill

	\hspace*{-0.1\columnwidth}
	\includegraphics[trim=0pt 15pt 10pt 15pt,clip,width=1.1\columnwidth]{scaling_time_pred}
	\caption{Experiment~3 results, displayed as a function of $N_0$. From top to bottom, $R^2$,
	$\overline{t}_{\text{trn.}}$, $\overline{t}_{\text{pred.}}$.}
	\label{fig:scaling}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.55}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.58}
	\end{minipage}
